### 2015-03-16 bugfinding.tex
updates in bug finding section

We use a simple, but effective, race checking instrumentation with \corral. This instrumentation is optional and we use it as a feasibility checking for the potential data races that \whoop reports.

>>>>

We use a simple, but effective, race checking instrumentation with \corral. This instrumentation, which is based on previous work~\cite{}, can be enabled using a command line option and we use it as a feasibility checking for the potential data races that \whoop reports. Whenever there is a write access, e.g. \texttt{\$M.13 := 0}, we instrument the Boogie IVL code as follows:

\begin{boogie}
$M.13 := 0;
yield;
assert $M.13 == 0;
\end{boogie}

Likewise, for a read access, e.g. \texttt{\$p0 := \$M.13}, we instrument the Boogie IVL code as follows:

\begin{boogie}
$p0 := $M.13;
yield;
$rv0 := $M.13;
assert $p0 == $rv0;
\end{boogie}

Our instrumentation tolerates benign races, as it will never report an assertion violation if there is a write-write race, where the two write accesses update the shared memory location with the same value.
